Tidy data structure to support exploration and modeling of temporal data

### 2018-11-20 main.Rmd
time-based pipeline needs more organisation

What is notable about an effective implementation of a data pipeline is that it coordinates a user's analysis making it cleaner to follow, and permits a wider audience to focus on the data analysis without getting lost in a jungle of computational intricacies. A fluent and fluid pipeline glues tidy data and the grammar of data manipulation together. It helps (1) break up a big problem to into manageable blocks, (2) generate human readable analysis workflow, (3) avoid introducing mistakes as many as possible.

@@

This tidy data representation choice will prove suitable for almost all conceivable applications of temporal data. Time-based pipeline starts with raw data however it arrives. It is advised to scrutinize identical entries of key and index in the right beginning. Duplicates signal the data quality issue, which would likely affect succeeding analyses and hence decision making. Analysts are encouraged to gaze at data as earlier as possible and reason about the process of data cleaning. When the data meets the tsibble standard, it flows into the exploration stage.

>>>>

What is notable about an effective implementation of a data pipeline is that it coordinates a user's analysis making it cleaner to follow, and permits a wider audience to focus on the data analysis without getting lost in a jungle of computational intricacies. A fluent and fluid pipeline glues tidy data and the grammar of data manipulation together. It helps (1) break up a big problem to into manageable blocks, (2) generate human readable analysis workflow, (3) avoid introducing mistakes, at least making it possible to trace them through the pipeline.

@@

XXX may be good to have a diagram here showing how the time-based pipeline builds on a regular data pipeline

XXX Put comments in above each paragraph, with the topic of each paragraph. its not clear how this section flows yet. the topics would help.

The time-based pipeline shepards raw temporal data through to time series analysis, and plots. It is advised to scrutinize identical entries of key and index in the right beginning. Duplicates signal the data quality issue, which would likely affect succeeding analyses and hence decision making. Analysts are encouraged to gaze at data as earlier as possible and reason about the process of data cleaning. When the data meets the tsibble standard, it flows into the exploration stage.
